A free/open-source machine translation system for English to Kazakh

### 2015-01-23 engkaz-eamt-2015/engkaz-eamt-2015.tex
about cg
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58557 72bbbca6-d526-0410-a7d9-f06f51895060

>>>>

Rules
Disambiguation rules

This kind of rules solves the problem of part-of-speech(POS) ambiguity by Constraint Grammar(CG) (Karlsson et al., 1995). The output of morphological analyser could be ambiguous, and in this case CG rules choose correct analysis from multiple analyses. From English to Kazakh POS ambiguity could be only in English side, but also some choices depends on Kazakh grammar.

Lexicon selection rules
